---
title: "Coronavirus Info Dashboard"
output: flexdashboard::flex_dashboard
runtime: shiny

---

```{r setup, include=FALSE}
library(flexdashboard); 
library(dplyr); library(plotly); library(rgdal); library(leaflet); library(magrittr); library(gtrendsR); library(stringr); library(ggplot2); library(tidyr); library(data.table)
```

About
===================================== 

Created by Bo Kim, Austin Gu, and Grace Windheim

The Coronavirus Info Dashboard is a user-friendly, interactive tool to monitor and visualize the COVID-19 pandemic from a variety of perspectives.


_**DISCLAIMER: This was created as part of a class project and should not be used as official health information.**_


Travel Restrictions data last updated on March 22, 2020. Data used to generate the Statistics and Trends tabs are updated continuously.


**Travel Restrictions**

Map displays countries with CDC Level 3 Travel Health Notice which states that nonessential travel to the following destinations should be avoided according to the CDC. 

* Use the +/- tabs to zoom in and out of the map. 

* Click and drag the map to re-orient. 

* Hover over the country of interest. 

* Red pins indicate countries with “Level 3 Travel Health Notice”

**Statistics**

Plots display total confirmed cases, total people recovered, and total deaths by day. 

* Hover over plot for date, value, and country 

* Double click country name to isolate plot of interest

* Top-right toolbar includes option to compare country data by hover 

**Trends**

Graphs display Google search hits for the term “coronavirus” over time and for popular queries related to “coronavirus.”

* Select time range to see results from the past hour, past day, past 7 days, past 30 days, etc. 

* Select results source to be all web, YouTube only, images only, or Froogle only.

* Hover over plots to display the relative popularity of the search term


1. Travel Restrictions
===================================== 
    
### Countries with CDC Level 3 Travel Health Notice

Nonessential travel to the following destinations should be avoided according to the CDC. Most foreign nationals who have entered these countries within the last 14 days will be barred entry to the United States. [Data sourced from the CDC](https://www.cdc.gov/coronavirus/2019-ncov/travelers/map-and-travel-notices.html)
```{r map}

download.file("http://thematicmapping.org/downloads/TM_WORLD_BORDERS_SIMPL-0.3.zip" , destfile="TM_WORLD_BORDERS_SIMPL-0.3.zip")

unzip("TM_WORLD_BORDERS_SIMPL-0.3.zip")

myspdf = readOGR(dsn=getwd(), layer="TM_WORLD_BORDERS_SIMPL-0.3", verbose = FALSE)
#head(myspdf)
#summary(myspdf)

content <- paste(sep = "<br/>",
                 "<b><a href = 'https://www.cdc.gov/coronavirus/2019-ncov/travelers/map-and-travel-notices.html'> CDC Geographic Risk Assessment for COVID-19 Transmission</a></b>", 
                 "Level 3 Travel Health Notice",
                 "Widespread ongoing transmission with restrictions on entry to the United States")

icons = awesomeIcons(icon = "bullhorn", library = "glyphicon",
                     markerColor = "red", iconColor = "white", spin = FALSE,
                     extraClasses = NULL, squareMarker = FALSE, iconRotate = 0,
                     fontFamily = "monospace", text = NULL)
  
leaflet(data=myspdf) %>% 
  addTiles() %>% 
  setView(lat=55, lng= 50 , zoom= 2) %>% 
  addPolygons(fillColor = "green", weight = 2,
              highlight = highlightOptions(weight = 2,
                                           color = "red",
                                           fillOpacity = 0.7,
                                            bringToFront = TRUE),
              label=~NAME) %>%
  addAwesomeMarkers(lat = c(35.9, 32.4, 47.5, 50.5, 49.8, 56.3, 58.6, 61.9, 46.2, 51.2, 39.1, 47.2, 64.9, 41.9, 56.9, 55.2, 49.8, 35.9, 52.1, 51.9, 39.4, 46.2, 48.7, 40.5, 60.1, 46.8, 43.7, 53.1), 
             lng = c(104.2, 53.7, 14.6, 4.5, 15.5, 9.5, 25, 25.7, 2.2, 10.5, 21.8, 19.5, 19.1, 12.6, 24.6, 23.9, 6.1, 14.4, 5.3, 19.1, 8.2, 15, 19.7, 3.7, 18.6, 8.2, 7.4, 7.7), 
             popup = content, icon = icons 
             )
```
    
2. Statistics {data-orientation=rows}
=====================================     
Row {.tabset .tabset-fade}
-------------------------------------
### Confirmed Cases
    
```{r}
#dat = read.csv("https://raw.githubusercontent.com/CSSEGISanddata/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv")

dat = read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")

dat = dat %>%
  rename_all(funs(str_replace(., "X", "")))

#dat

dat = dat %>%
  select(-Lat, -Long, -Province.State) %>%
  group_by(Country.Region) %>%
  summarise_all(sum) 

dat = dat %>%
  mutate(total_cases = rowSums(dat[2:ncol(dat)])) %>%
  arrange(desc(total_cases)) %>%
  head(20) 

dat2 = dat %>%
  select(-total_cases) 

setnames(dat2, old = colnames(dat2[, 2:ncol(dat2)]), new = as.character(as.Date(colnames(dat2[, 2:ncol(dat2)]), format = "%m.%d.%y")))

dat.long = gather(dat2, colnames(dat2[,2:ncol(dat2)]), key = "date", value = "cases")
#dat.long

plot = ggplot(dat.long, aes(x = date, y = cases, col = Country.Region, group = 1))
plot = plot + geom_line() + theme(axis.text.x=element_text(angle=90,hjust=1)) + ggtitle("Total Confirmed Cases by Day")

ggplotly(plot)

```
   
### Recovered Cases
    
```{r}
#dat.rec = read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv")

dat.rec = read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv")

dat.rec = dat.rec %>%
  rename_all(funs(str_replace(., "X", "")))

dat.rec = dat.rec %>%
  select(-Lat, -Long, -Province.State) %>%
  group_by(Country.Region) %>%
  summarise_all(sum) 

dat.rec = dat.rec %>%
  mutate(total_recovered = rowSums(dat.rec[2:ncol(dat.rec)])) %>%
  arrange(desc(total_recovered)) %>%
  head(20) 

dat2.rec = dat.rec %>%
  select(-total_recovered) 

setnames(dat2.rec, old = colnames(dat2.rec[, 2:ncol(dat2.rec)]), new = as.character(as.Date(colnames(dat2.rec[, 2:ncol(dat2.rec)]), format = "%m.%d.%y")))

dat.long.rec = gather(dat2.rec, colnames(dat2.rec[,2:ncol(dat2.rec)]), key = "date", value = "recovered") 
#dat.long

plot.rec = ggplot(dat.long.rec, aes(x = date, y = recovered, col = Country.Region, group = 1))
plot.rec = plot.rec + geom_line() + theme(axis.text.x=element_text(angle=90,hjust=1)) + ylab("Total Recovered") + ggtitle("Total People Recovered by Day")

ggplotly(plot.rec)
```
  

### Deaths
    
```{r}
#dat.deaths = read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv")

dat.deaths = read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")

dat.deaths = dat.deaths %>%
  rename_all(funs(str_replace(., "X", "")))

#dat.deaths

dat.deaths = dat.deaths %>%
  select(-Lat, -Long, -Province.State) %>%
  group_by(Country.Region) %>%
  summarise_all(sum) 

dat.deaths = dat.deaths %>%
  mutate(total_deaths = rowSums(dat.deaths[2:ncol(dat.deaths)])) %>%
  arrange(desc(total_deaths)) %>%
  head(20) 

dat2.deaths = dat.deaths %>%
  select(-total_deaths) 

setnames(dat2.deaths, old = colnames(dat2.deaths[, 2:ncol(dat2.deaths)]), new = as.character(as.Date(colnames(dat2.deaths[, 2:ncol(dat2.deaths)]), format = "%m.%d.%y")))

dat.long.deaths = gather(dat2.deaths, colnames(dat2.deaths[,2:ncol(dat2.deaths)]), key = "date", value = "deaths")
#dat.long.deaths

plot.deaths = ggplot(dat.long.deaths, aes(x = date, y = deaths, col = Country.Region, group = 1))
plot.deaths = plot.deaths + geom_line() + theme(axis.text.x=element_text(angle=90,hjust=1)) + ylab("Total Deaths") + ggtitle("Total Deaths by Day")

ggplotly(plot.deaths)
```

3. Trends
=====================================      
   
Column {data-width=350}
-------------------------------------
    
### Inputs

_**Graphics may take a few moments to load, please be patient! If an error message is shown, that means no data has been found - try another search.**_  

Graphs are plotted on a relative scale and times are shown in Coordinated Universal Time (UTC).

Data is sourced from Google Trends and retrieved through the gtrendsR package. 

```{r select}

selectInput("time", "Show results from the: ",
                c("Past hour" = "now 1-H",
                  "Past day"= "now 1-d",
                  "Past 7 days" = "now 7-d",
                  "Past 30 days" = "today 1-m",
                  "Past 90 days" = "today 3-m",
                  "Past 12 months" = "today 12-m",
                  "Past 5 years" = "today+5-y"
                  ), selected = "now 1-H")


selectInput("source", "Source results from: ",
            c("All web" = "web",
              "YouTube only" = "youtube",
              "Images only" = "images",
              "Froogle only" = "froogle"),
            selected = "web")

```
   
Column {.tabset}
-------------------------------------
   
### Search hits for "coronavirus"

```{r interest}

y = reactive({gtrends("coronavirus", time = input$time, gprop = input$source)})

renderPlotly({
  #y = gtrends("coronavirus", time = input$time, gprop = input$source)
  plot(y())
})
```   
 
### Popular queries related to "coronavirus"
    
```{r related}

  renderPlotly({
    #x = gtrends("coronavirus", time = input$time, gprop = input$source)
      
      queries = y()$related_queries %>% filter(subject >= 1)
      queries$subject = as.numeric(queries$subject) # make number
      queries = na.omit(queries)
      
      queries$value <- factor(queries$value, levels = unique(queries$value)[order(queries$subject, decreasing = FALSE)]) # order
      
      x <- list(title = "Search hits")
      y <- list(title = "Related query")
      fig = plot_ly(queries, x = ~subject, y = ~value, type = 'bar', name = "Related queries", marker = list(color = '#9119b8')) 
      fig = fig %>% layout(xaxis = x, yaxis = y)
      
      fig
    
  })
```

